BART: A Comparison with Non-bayesian Tree Methods

### 2025-01-03 paper/paper.tex
cleaned repo

\subsection{Pros and Cons of decision trees}
Overall, CART offers much greater flexibility in handling the relation between covariates and output than linear models do. This comes from the fact that fitting a regression tree amounts to estimate a stepwise relation between $y$ and the covariates $x$ that can proxy well non-linear patterns. 
\\\\Greater flexibility of CART comes in handy also when dealing with missing values. CART offers an effective way to overcome this issue, by constructing surrogate variables. Exploiting correlation between predictors, CART may decrease the effect of missing data.

@@

\subsection{Random Forest}
A possible problem with bagging is due to the lack of randomization between trees. Indeed, since trees are separately fitted on the bootstrapped training set, it may happen that they share to great amount the same decision rule. This is the case, for example, if there is very strong predictor in the dataset. Hence, in the collection of bagged trees a vast majority of the trees will use this strong predictor in the top split and tehy will all be hihgly correlated among themselves.
\\Correlation among the trees in turn decrease the effectiveness of averaging, as it does not lead to a large reduction in variance, making the entire bagging algorithm less useful. 
\\\\ Random Forests starts from bagging and adds another kind of randomization to reduce correlation among trees. Rather than searching over all the covariate space for each decision rule, as the greedy build of the big trees imposes, in random forests we randomly sample a subset of $m$ covariates to search over each time we make a split. Therefore, the split is allowed to consider only one of those m predictors. Moreover, at each split is considered a new sample of m predictors. This makes the big trees explore more the space of models
\\\\Usually, we choose $m \approx \sqrt{p}$.
On average, $(p - m)/ = p$ of the splits will not even consider the strong predictor, and so other predictors will have more of a chance. Therefore, we can think of this process as decorrelating the trees, making the average of the resulting trees less variable and hence more reliable.

@@

By fitting sequentially new trees on the residual of the previous tree, voosting improves at each iteration the fit marginally. Indeed, since there is a constraining parameter $\lambda$, each tree is rather small, with just a few terminal nodes. By 
fitting small trees to the residuals, we slowly improve $\hat{f}$ in areas where it
does not perform well. It is important to mention that in boosting, unlike in bagging, the construction of each tree strongly depends on the trees that have already grown.
\\\\The model accounts for three different tuning parameters. The number of of trees $B$, chosen trough cross-validation.  Interestingly, unlike bagging and random forests, boosting can suffer of overfitting if $B$ is too large.
The shrinkage parameter $\lambda$, a small positive number. Common values for $\lambda$ are 0.01 or 0.001, depending on the problem at hand. However, very small values of $\lambda$ often require a very large B to achieve good performances. Lastly, $d$ represents the number of splits in each tree. Often $d=1$ works well. However in this case the tree is called stump since it contains only a single split.

\section{Bayesian additive regression trees (BART)}
The idea for Bayesian Additive Regression Trees (BART) was first developed by Chipman, George, McCulloch (2010 AOAS). Like other ensemble methods (bagging, boosting, random forest), to solve this regression problem \eqref{regression}, BART approximates \( f(x) = \mathbb{E}(y \mid x) \) by a sum of $m$ regression trees \( h(x) \equiv \sum_{j=1}^m g(x, T_j, M_j)\), where each \( g \) is a regression tree function that given a tree $\theta_j$ to each observation $x$  assigns a leaf $\mu_{ij}$ of that regression tree.
\\\\The BART Ensemble Model is therefore
\[
y = \sum_{j=1}^m g(x; T_j, M_j) + \epsilon, \quad \epsilon \sim N(0, \sigma^2) \tag{3}
\]
where for each binary regression tree \( T_j \) and its associated terminal node parameters \( M_j \), \( g(x; T_j, M_j) \) is the function which assigns \( \mu_{ij} \in M_j \) to \( x \). Under \((3)\), \( \mathbb{E}(y \mid x) \) equals the sum of all the terminal node \( \mu_{ij} \)'s assigned to \( x \) by the \( g(x; T_j, M_j) \)'s.
\\\\Like the other ensemble methods, to avoid overfitting each tree of the summation must be made a weak learner, explaining only part of the result. To do so, while boosting uses a shrinkage parameter $\lambda$, BART uses a regularization prior:
\[
p((T_1, M_1), (T_2, M_2), \ldots, (T_m, M_m), \sigma)
\]
The prior is set in a way to regularize the fit by keeping the individual tree effects small. It forces each tree to explain only a limited subset of the relationships between the covariates and the predictor variable (it is a marginal addition to the overall fit). By weakening the \( g_j \) effects, BART ends up with a sum of trees, each of which explains a small and different portion of \( f \).

@@

\\\\Overall, Bart's characteristics are in how it weakens the individual trees by instead using a prior, and how it performs the iterative fitting by instead using Bayesian backfitting on a fixed number of trees. 
Conceptually, BART can be viewed as a Bayesian nonparametric approach that fits a parameter-rich model using a strongly influential prior distribution. Overall, BART is a highly-dimensional (each tree has unknown size) nonlinear model inspired by boosting and tree ensembles. the main difference is that, being Bayesian, it uses a regularization prior to shrink towards a simple model. It uses MCMC to get draws from the high dimensional posterior so that one can stochastically search the  model space and gauge the uncertainty.

@@

\subsubsection{A Sum-of-Trees Model}
Denote by \( T \) the tree structure, consisting of a set of interior node decision rules and a set of $b$ terminal nodes. The decision rules are binary splits of the predictor space of the form \( \{x \in A\} \) vs \( \{x \notin A\} \), where \( A \) is a subset of the range of \( x \). We only consider rules based on the single components of \( x = (x_1, \dots, x_p) \) and of the form \( \{x_i \leq c\} \) vs \( \{x_i > c\} \) for continuous \( x_i \). Let \( M = \{\mu_1, \mu_2, \dots, \mu_b\} \) denote a set of parameter values associated with each of the \( b \) terminal nodes of \( T \). Given the way it is constructed, the tree is a full binary tree, that is, each node has exactly zero or two children. 
\\\\ Let \( g(x; T, M) \) denote the regression tree function which assigns a \( \mu_i \in M \) to \( x \).
Each \( x \) value is associated with a single terminal node of \( T \) by the sequence of decision rules from top to bottom, and is then assigned the \( \mu_i \) value associated with this terminal node. 
\\\\We denote by \( T \) the binary tree structure itself—the various binary split decision rules of the form \( \{x_q < c\} \) versus \( \{x_q \geq c\} \), \( c \in \mathbb{R} \). The vector of parameters associated with \( T \), i.e., the collection of terminal node parameters, is denoted by \( M = \{\mu_1, \ldots, \mu_b\} \), where \( b \) is the number of terminal nodes. Defining a regression tree as \( g(x; T, M) \), we can view \( g(x; T, M) \) as a function that assigns the conditional mean \( \mathbb{E}[y \mid x] \) to the parameter \( \mu_i \in M \), i.e., \( \mu_i = g(x; T, M) \rightarrow \mathbb{E}[y \mid x] \) via binary decision rules denoted as \( T \).
\\\\Thus,
\begin{equation}
Y = g(x; T, M) + \epsilon, \quad \epsilon \sim N(0, \sigma^2)
\end{equation}
is a single tree model. Under (3), the conditional mean of \( Y \) given \( x \), \( \mathbb{E}(Y \mid x) \), equals the terminal node parameter \( \mu \) assigned by \( g(x \mid T, M) \).
With this notation, the sum-of-trees model can be more explicitly expressed as
\begin{equation}
Y = \sum_{j=1}^m g(x; T_j, M_j) + \epsilon, \quad \epsilon \sim N(0, \sigma^2) \label{likelihood}
\end{equation}
where for each binary regression tree \( T_j \) and its associated terminal node parameters \( M_j \), \( g(x; T_j, M_j) \) is the function which assigns \( \mu_{j} \in M_j \) to \( x \). Under (4), \( \mathbb{E}(Y \mid x) \) equals the sum of all the terminal node \( \mu_{j} \)'s assigned by the \( g(x \mid T_j, M_j) \)'s. When the number of trees \( m > 1 \), each \( g(x; T_j, M_j) \) here is merely a part of \( \mathbb{E}(Y \mid x) \), unlike the single tree model.
\\\\We can see that the quantity that is being ``summed'' and eventually allocated to \( \mathbb{E}(y \mid x) \) is not the regression tree or tree structure, but the value that each \( j \)th tree structure assigns to the subject. This is one way to think of a sum of regression trees. It allocates a sum of parameters \( \mu_{j} \) to \( \mathbb{E}[y \mid x] \) of the subject.

\\\\A sum-of-trees model is an additive function, a sum of step functions of the individual components of \( x \). With a large number of trees, a sum-of-trees model gains increased representation flexibility which, as we'll see, endows BART with excellent predictive capabilities. This representational flexibility is obtained by rapidly increasing the number of parameters. Indeed, for fixed \( m \), each sum-of-trees model (4) is determined by \( (T_1, M_1), \ldots, (T_m, M_m) \) and \( \sigma \), which includes all the bottom node parameters as well as the tree structures and decision rules. Further, the representational flexibility of each individual tree leads to substantial redundancy across the tree components. Indeed, one can regard \( \{g(x; T_1, M_1), \ldots, g(x; T_m, M_m)\} \) as an "overcomplete basis" in the sense that many different choices of \( (T_1, M_1), \ldots, (T_m, M_m) \) can lead to an identical function \( \sum_{j=1}^m g(x; T_j, M_j) \).

\\\\\textbf{Nonlinearity of BART.} From this simple example, we can see how BART handles nonlinearity. Each single regression tree is a simple stepwise function or ANOVA model. When we sum regression trees together, we are actually summing together these ANOVA models or stepwise functions, and as a result, we eventually obtain a more complicated stepwise function that can approximate the nonlinearities in the main effect and multiple-way interactions.

@@

\\\\The BART model specification is completed by imposing a prior over all the parameters of the sum-of-trees model, namely, \( (T_1, M_1), \ldots, (T_m, M_m) \) and \( \sigma \). There exist specifications of this prior that effectively regularize the fit by keeping the individual tree effects from being unduly influential. Without such a regularizing influence, large tree components would overwhelm the rich structure of (3), thereby limiting the advantages of the additive representation both in terms of function approximation and computation.

@@

where \( \mu_{ij} \in M_j \) where \( \mu_i \sim p(\mu) \), iid.
Finally we can write the prior distribution for \eqref{likelihood} as:
\[
p[(T_1, M_1), \ldots, (T_m, M_m), \sigma]= \left[ \prod_{j=1}^m \left( \prod_{i=1}^{b_j} p(\mu_{ji} \mid T_j) \right) \right] \, p(\sigma) \, p(T_j).
\]
Under the independence assumption, we only need to specify \( p(T_j) \), \( p(\mu_{ij} \mid T_j) \), and \( p(\sigma) \). Note that we want to have each $T$ small, each $\mu$ small,  and a "nice " $\sigma$  (e.g. smaller than the least squares estiamte). Indeed, we refer to $p$ as the regularization prior as it restraints the overall fit. In addition, it keeps the contribution of each $g(x;T_i,M_i)$ model component small.  
\\\\
\textbf{The $T_j$ prior}
The trees $T_j$ are assumed to be iid, so that it is sufficient to define a single $p(T_j)$. Chipman specifies a process 
 that can be used to fraw a tree from the prior. The \( T_j \) prior, \( p(T_j) \), is specified by three aspects:
\begin{enumerate}
    \item The probability that a node at depth \( d = (0, 1, 2, \ldots) \) is nonterminal, given by:
    \[
    \alpha (1 + d)^\beta \quad \text{with} \quad \alpha \in (0, 1) \quad \text{and} \quad \beta \in [0, \infty).
    \]
    Node depth is defined as the distance from the root. Thus, the root itself has depth 0, its first child node has depth 1, etc. This prior controls the tree depth. For a sum-of-trees model with \( m \) large, we want the regularization prior to keep the individual tree components small. To do that, we usually use \( \alpha = 0.95 \) and \( \beta = 2 \).  This makes nonnull but small tree more likely. Nonetheless,  trees with many terminal nodes can be grown if the data demands it.

@@

\\\\\\\\Or (\(^ {17}\)), we use the conjugate normal distribution \(N(\mu, \sigma^2)\), which offers tremendous computational benefits because \(\mu\) can be marginalized out.

@@

\\\\\\\\The choice of \(m\). A major difference between BART and boosting methods is that, for a fixed number of trees \(m\), BART uses an iterative backfitting algorithm to cycle over and over through the \(m\) trees.
BART involves many parameters to ensure flexibility in modeling. Unlike boosting and random forests, the BART algorithm iteratively updates a fixed set of \(m\) trees. A strong prior is used to shrink the model towards simple structures, effectively regularizing the model and encouraging it to align with additive models that incorporate some level of interaction.

>>>>

\subsection{Pros and Cons of decision trees}
Overall, CART offers much greater flexibility in handling the relation between covariates and output than linear models do. This comes from the fact that fitting a regression tree amounts to estimate a stepwise relation between $y$ and the covariates $x$ that can proxy well non-linear patterns. 
Greater flexibility of CART comes in handy also when dealing with missing values. CART offers an effective way to overcome this issue, by constructing surrogate variables. Exploiting correlation between predictors, CART may decrease the effect of missing data.

@@

\subsection{Random Forest}
A possible problem with bagging is due to the lack of randomization between trees. Indeed, since trees are separately fitted on the bootstrapped training set, it may happen that they share to great amount the same decision rule. This is the case, for example, if there is very strong predictor in the dataset. Hence, in the collection of bagged trees a vast majority of the trees will use this strong predictor in the top split and tehy will all be hihgly correlated among themselves.
\\Correlation among the trees in turn decrease the effectiveness of averaging, as it does not lead to a large reduction in variance, making the entire bagging algorithm less useful. 
 Random Forests starts from bagging and adds another kind of randomization to reduce correlation among trees. Rather than searching over all the covariate space for each decision rule, as the greedy build of the big trees imposes, in random forests we randomly sample a subset of $m$ covariates to search over each time we make a split. Therefore, the split is allowed to consider only one of those m predictors. Moreover, at each split is considered a new sample of m predictors. This makes the big trees explore more the space of models
Usually, we choose $m \approx \sqrt{p}$.
On average, $(p - m)/ = p$ of the splits will not even consider the strong predictor, and so other predictors will have more of a chance. Therefore, we can think of this process as decorrelating the trees, making the average of the resulting trees less variable and hence more reliable.

@@

By fitting sequentially new trees on the residual of the previous tree, voosting improves at each iteration the fit marginally. Indeed, since there is a constraining parameter $\lambda$, each tree is rather small, with just a few terminal nodes. By 
fitting small trees to the residuals, we slowly improve $\hat{f}$ in areas where it
does not perform well. It is important to mention that in boosting, unlike in bagging, the construction of each tree strongly depends on the trees that have already grown.
The model accounts for three different tuning parameters. The number of of trees $B$, chosen trough cross-validation.  Interestingly, unlike bagging and random forests, boosting can suffer of overfitting if $B$ is too large.
The shrinkage parameter $\lambda$, a small positive number. Common values for $\lambda$ are 0.01 or 0.001, depending on the problem at hand. However, very small values of $\lambda$ often require a very large B to achieve good performances. Lastly, $d$ represents the number of splits in each tree. Often $d=1$ works well. However in this case the tree is called stump since it contains only a single split.

\section{Bayesian additive regression trees (BART)}
The idea for Bayesian Additive Regression Trees (BART) was first developed by Chipman, George, McCulloch (2010 AOAS). Like other ensemble methods (bagging, boosting, random forest), to solve this regression problem \eqref{regression}, BART approximates \( f(x) = \mathbb{E}(y \mid x) \) by a sum of $m$ regression trees \( h(x) \equiv \sum_{j=1}^m g(x, T_j, M_j)\), where each \( g \) is a regression tree function that given a tree $\theta_j$ to each observation $x$  assigns a leaf $\mu_{ij}$ of that regression tree.
The BART Ensemble Model is therefore
\[
y = \sum_{j=1}^m g(x; T_j, M_j) + \epsilon, \quad \epsilon \sim N(0, \sigma^2) \tag{3}
\]
where for each binary regression tree \( T_j \) and its associated terminal node parameters \( M_j \), \( g(x; T_j, M_j) \) is the function which assigns \( \mu_{ij} \in M_j \) to \( x \). Under \((3)\), \( \mathbb{E}(y \mid x) \) equals the sum of all the terminal node \( \mu_{ij} \)'s assigned to \( x \) by the \( g(x; T_j, M_j) \)'s.
Like the other ensemble methods, to avoid overfitting each tree of the summation must be made a weak learner, explaining only part of the result. To do so, while boosting uses a shrinkage parameter $\lambda$, BART uses a regularization prior:
\[
p((T_1, M_1), (T_2, M_2), \ldots, (T_m, M_m), \sigma)
\]
The prior is set in a way to regularize the fit by keeping the individual tree effects small. It forces each tree to explain only a limited subset of the relationships between the covariates and the predictor variable (it is a marginal addition to the overall fit). By weakening the \( g_j \) effects, BART ends up with a sum of trees, each of which explains a small and different portion of \( f \).

@@

Overall, Bart's characteristics are in how it weakens the individual trees by instead using a prior, and how it performs the iterative fitting by instead using Bayesian backfitting on a fixed number of trees. 
Conceptually, BART can be viewed as a Bayesian nonparametric approach that fits a parameter-rich model using a strongly influential prior distribution. Overall, BART is a highly-dimensional (each tree has unknown size) nonlinear model inspired by boosting and tree ensembles. the main difference is that, being Bayesian, it uses a regularization prior to shrink towards a simple model. It uses MCMC to get draws from the high dimensional posterior so that one can stochastically search the  model space and gauge the uncertainty.

@@

\subsubsection{A Sum-of-Trees Model}
Denote by \( T \) the tree structure, consisting of a set of interior node decision rules and a set of $b$ terminal nodes. The decision rules are binary splits of the predictor space of the form \( \{x \in A\} \) vs \( \{x \notin A\} \), where \( A \) is a subset of the range of \( x \). We only consider rules based on the single components of \( x = (x_1, \dots, x_p) \) and of the form \( \{x_i \leq c\} \) vs \( \{x_i > c\} \) for continuous \( x_i \). Let \( M = \{\mu_1, \mu_2, \dots, \mu_b\} \) denote a set of parameter values associated with each of the \( b \) terminal nodes of \( T \). Given the way it is constructed, the tree is a full binary tree, that is, each node has exactly zero or two children. 
 Let \( g(x; T, M) \) denote the regression tree function which assigns a \( \mu_i \in M \) to \( x \).
Each \( x \) value is associated with a single terminal node of \( T \) by the sequence of decision rules from top to bottom, and is then assigned the \( \mu_i \) value associated with this terminal node. 
We denote by \( T \) the binary tree structure itself—the various binary split decision rules of the form \( \{x_q < c\} \) versus \( \{x_q \geq c\} \), \( c \in \mathbb{R} \). The vector of parameters associated with \( T \), i.e., the collection of terminal node parameters, is denoted by \( M = \{\mu_1, \ldots, \mu_b\} \), where \( b \) is the number of terminal nodes. Defining a regression tree as \( g(x; T, M) \), we can view \( g(x; T, M) \) as a function that assigns the conditional mean \( \mathbb{E}[y \mid x] \) to the parameter \( \mu_i \in M \), i.e., \( \mu_i = g(x; T, M) \rightarrow \mathbb{E}[y \mid x] \) via binary decision rules denoted as \( T \).
Thus,
\begin{equation}
Y = g(x; T, M) + \epsilon, \quad \epsilon \sim N(0, \sigma^2)
\end{equation}
is a single tree model. Under (3), the conditional mean of \( Y \) given \( x \), \( \mathbb{E}(Y \mid x) \), equals the terminal node parameter \( \mu \) assigned by \( g(x \mid T, M) \).
With this notation, the sum-of-trees model can be more explicitly expressed as
\begin{equation}
Y = \sum_{j=1}^m g(x; T_j, M_j) + \epsilon, \quad \epsilon \sim N(0, \sigma^2) \label{likelihood}
\end{equation}
where for each binary regression tree \( T_j \) and its associated terminal node parameters \( M_j \), \( g(x; T_j, M_j) \) is the function which assigns \( \mu_{j} \in M_j \) to \( x \). Under (4), \( \mathbb{E}(Y \mid x) \) equals the sum of all the terminal node \( \mu_{j} \)'s assigned by the \( g(x \mid T_j, M_j) \)'s. When the number of trees \( m > 1 \), each \( g(x; T_j, M_j) \) here is merely a part of \( \mathbb{E}(Y \mid x) \), unlike the single tree model.
We can see that the quantity that is being ``summed'' and eventually allocated to \( \mathbb{E}(y \mid x) \) is not the regression tree or tree structure, but the value that each \( j \)th tree structure assigns to the subject. This is one way to think of a sum of regression trees. It allocates a sum of parameters \( \mu_{j} \) to \( \mathbb{E}[y \mid x] \) of the subject.

A sum-of-trees model is an additive function, a sum of step functions of the individual components of \( x \). With a large number of trees, a sum-of-trees model gains increased representation flexibility which, as we'll see, endows BART with excellent predictive capabilities. This representational flexibility is obtained by rapidly increasing the number of parameters. Indeed, for fixed \( m \), each sum-of-trees model (4) is determined by \( (T_1, M_1), \ldots, (T_m, M_m) \) and \( \sigma \), which includes all the bottom node parameters as well as the tree structures and decision rules. Further, the representational flexibility of each individual tree leads to substantial redundancy across the tree components. Indeed, one can regard \( \{g(x; T_1, M_1), \ldots, g(x; T_m, M_m)\} \) as an "overcomplete basis" in the sense that many different choices of \( (T_1, M_1), \ldots, (T_m, M_m) \) can lead to an identical function \( \sum_{j=1}^m g(x; T_j, M_j) \).

\textbf{Nonlinearity of BART.} From this simple example, we can see how BART handles nonlinearity. Each single regression tree is a simple stepwise function or ANOVA model. When we sum regression trees together, we are actually summing together these ANOVA models or stepwise functions, and as a result, we eventually obtain a more complicated stepwise function that can approximate the nonlinearities in the main effect and multiple-way interactions.

@@

The BART model specification is completed by imposing a prior over all the parameters of the sum-of-trees model, namely, \( (T_1, M_1), \ldots, (T_m, M_m) \) and \( \sigma \). There exist specifications of this prior that effectively regularize the fit by keeping the individual tree effects from being unduly influential. Without such a regularizing influence, large tree components would overwhelm the rich structure of (3), thereby limiting the advantages of the additive representation both in terms of function approximation and computation.

@@

where \( \mu_{ij} \in M_j \) where \( \mu_i \sim p(\mu) \), iid.
Finally we can write the prior distribution for \eqref{likelihood} as:
\[
p[(T_1, M_1), \ldots, (T_m, M_m), \sigma]= \left[ \prod_{j=1}^m \left( \prod_{i=1}^{b_j} p(\mu_{ji} \mid T_j) \right) \right] \, p(\sigma) \, p(T_j).
\]
Under the independence assumption, we only need to specify \( p(T_j) \), \( p(\mu_{ij} \mid T_j) \), and \( p(\sigma) \). Note that we want to have each $T$ small, each $\mu$ small,  and a "nice " $\sigma$  (e.g. smaller than the least squares estiamte). Indeed, we refer to $p$ as the regularization prior as it restraints the overall fit. In addition, it keeps the contribution of each $g(x;T_i,M_i)$ model component small.

\textbf{The $T_j$ prior}
The trees $T_j$ are assumed to be iid, so that it is sufficient to define a single $p(T_j)$. Chipman specifies a process 
 that can be used to fraw a tree from the prior. The \( T_j \) prior, \( p(T_j) \), is specified by three aspects:
\begin{enumerate}
    \item The probability that a node at depth \( d = (0, 1, 2, \ldots) \) is nonterminal, given by:
    \[
    \alpha (1 + d)^\beta \quad \text{with} \quad \alpha \in (0, 1) \quad \text{and} \quad \beta \in [0, \infty).
    \]
    Node depth is defined as the distance from the root. Thus, the root itself has depth 0, its first child node has depth 1, etc. This prior controls the tree depth. For a sum-of-trees model with \( m \) large, we want the regularization prior to keep the individual tree components small. To do that, we usually use \( \alpha = 0.95 \) and \( \beta = 2 \).  This makes nonnull but small tree more likely. Nonetheless,  trees with many terminal nodes can be grown if the data demands it.

@@

Or (\(^ {17}\)), we use the conjugate normal distribution \(N(\mu, \sigma^2)\), which offers tremendous computational benefits because \(\mu\) can be marginalized out.

@@

The choice of \(m\). A major difference between BART and boosting methods is that, for a fixed number of trees \(m\), BART uses an iterative backfitting algorithm to cycle over and over through the \(m\) trees.
BART involves many parameters to ensure flexibility in modeling. Unlike boosting and random forests, the BART algorithm iteratively updates a fixed set of \(m\) trees. A strong prior is used to shrink the model towards simple structures, effectively regularizing the model and encouraging it to align with additive models that incorporate some level of interaction.
